\documentclass[11pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage{booktabs}
\usepackage{array}
\usepackage{xcolor}
\usepackage{fancyhdr}
\usepackage{lastpage}

% Define LMU colors
\definecolor{lmublue}{RGB}{0,91,165}

% Section formatting
\titleformat{\section}{\normalfont\Large\bfseries\centering}{}{0em}{}
\titleformat{\subsection}{\normalfont\large\bfseries}{}{0em}{}
\titleformat{\subsubsection}{\normalfont\normalsize\bfseries}{}{0em}{}

% Hyperlink setup
\hypersetup{
    colorlinks=true,
    linkcolor=lmublue,
    urlcolor=lmublue
}

% Header/Footer
\pagestyle{fancy}
\fancyhf{}
\renewcommand{\headrulewidth}{0pt}
\fancyfoot[C]{\thepage}

\begin{document}

%% ============================================================================
%% COVER PAGE 1
%% ============================================================================
\thispagestyle{empty}

\begin{center}
{\Large\bfseries\color{lmublue} Loyola Marymount University}\\[0.5em]
{\large\itshape Executive Vice President and Provost}
\end{center}

\vspace{1.5em}

\noindent\begin{tabular}{@{}ll}
\textbf{DATE:} & November 20, 2025 \\[0.5em]
\textbf{TO:} & Full-Time Tenured/Tenure-Track Faculty \\[0.5em]
\textbf{FROM:} & Kathleen Weaver \\
& Interim Executive Vice President and Provost \\[0.5em]
\textbf{SUBJECT:} & \textbf{Faculty Service Report - Calendar Year 2025} \\
\end{tabular}

\vspace{0.5em}
\noindent\rule{\textwidth}{0.4pt}
\vspace{1em}

Below please find your Faculty Service Report form for the calendar year 2025. This form is also available at \url{https://academics.lmu.edu/ofd/promotionsfsr/}. This form is intended to help you document your achievements during the past year and, when completed, will provide the basis for your evaluation by your department Chair and Dean. If you are serving as a department Chair or Associate Dean, then the completed 2025 Faculty Service Report is due to your Dean or their designee.

\vspace{1em}
\noindent\textbf{The suggested page limit is either 6-pages or defer to your college's page limits. Faculty may also receive a specific reporting format required by their Dean.}

\vspace{1em}
Each department Chair and Dean will evaluate the faculty member's total contribution. This will provide an opportunity for you to reflect upon your total contribution to the University, among your peers, and within your discipline or field during the year, and to consider any areas where you would like to increase your involvement.

\vspace{1em}
As per Faculty Handbook (III.A), faculty who do not submit an FSR will be ineligible for merit pay. This would include any faculty compensation tied to merit, such as has been stipulated in past equity increases. A specific timetable follows to inform your completion of the report for discussion with your department Chair. Please meet the specific dates in the timetable, to allow preparation of the 2026-2027 contracts on schedule.

\vspace{1em}
\begin{itemize}[leftmargin=*]
\item \textbf{February 5, 2026:} Completed 2025 Faculty Service Report due to your department Chair (or to your Dean/their designee if you are serving as department Chair or Associate Dean).

\item \textbf{February 11 -- March 9, 2026:} ``The department Chair will meet privately with each member of the faculty to review services through the past year. At this meeting the department Chair will discuss the faculty member's self-evaluation and service as described in the Faculty Service Report. The department Chair will comment on the faculty member's overall performance. No determination as to merit is to be made at this meeting. Merit recommendations will be made only after the review of all department faculty.'' (Faculty Handbook, 2025, III. C. b., pg.16)

\textbf{At least two business days prior to the meeting with an individual faculty member, the department Chair will provide the faculty member with a}
\end{itemize}

\newpage

%% ============================================================================
%% COVER PAGE 2
%% ============================================================================
\thispagestyle{empty}

\noindent\textbf{written report and evaluation.} After the meeting, the department Chair and individual faculty member are expected to sign and date the written report and evaluation to acknowledge that a discussion of the written report and evaluation took place. The department Chair will provide a copy of the written report and evaluation signed by both parties to the individual faculty member for their records and will also forward to the Dean. If the individual faculty member does not want to provide a signature on the written report and evaluation, then they are asked to provide a letter of dissent which should be signed and attached to the written report and evaluation.

\vspace{1em}
\begin{itemize}[leftmargin=*]
\item \textbf{February 11 -- March 20, 2026:} ``The department Chair will meet with the Dean and discuss the evaluation and ranking for each member of the department and the merit recommendations to be made to the Provost.'' (Faculty Handbook, 2025, III. C. c., pg. 16)

\vspace{0.5em}
``The Dean will review the recommendations of all department Chairs and will recommend the amount of merit to be given to each member of the faculty.'' (Faculty Handbook, 2025, III. C. d., pg. 16)

\vspace{0.5em}
If the Dean's recommendation to the Provost differs from the Chair's recommendation, the Dean must notify the faculty member in writing before making a recommendation to the Provost.

\vspace{0.5em}
\textbf{March 20, 2026:} Dean sends merit recommendations to Provost.
\end{itemize}

\newpage

%% ============================================================================
%% TEACHING / ADVISING
%% ============================================================================
\section*{TEACHING / ADVISING}

\vspace{1em}

\begin{center}
\begin{tabular}{llcc}
\toprule
\textbf{Semester} & \textbf{Course Number} & \textbf{Enrollment} & \textbf{Units} \\
\midrule
Spring 2025 & CMSI 2130 & 23 & 4 \\
Spring 2025 & CMSI 6998 & 6 & 3 \\
Fall 2025 & CMSI 2130 & 12 & 4 \\
Fall 2025 & CMSI 2130 & 38 & 4 \\
\bottomrule
\end{tabular}
\end{center}

\vspace{1em}

In 2025, my teaching and advising activities expanded significantly, emphasizing research mentorship and innovative pedagogy. I taught three sections of Algorithms \& Analysis and launched a new graduate special topics course on Decentralized Algorithms. My advising efforts resulted in multiple student presentations at national and international conferences, and I hired several undergraduate and graduate research assistants through external grant funding. These activities directly support LMU's mission by fostering inclusive, research-driven education and providing students from diverse backgrounds with opportunities to engage in cutting-edge scholarship.

\subsection*{Teaching Activities}

\begin{itemize}[leftmargin=*]
\item \textbf{Taught:} \textit{Algorithms \& Analysis} (CMSI 2130) in both Spring and Fall 2025 semesters
\item \textbf{Launched New Graduate Course:} \textit{Online and Decentralized Algorithms} (CMSI 6998) in Fall 2025, integrating theoretical foundations with real-world applications in distributed systems
\item \textbf{Pre-College Summer Program:} Ran a two-week ``Python for AI-Powered Applications'' course (June 23--July 3, 2025) for LMU's pre-college summer program, introducing high school students to programming and AI concepts
\end{itemize}

\subsubsection*{Course Evaluation Summary}

Across 4 course sections with 54 student responses (68\% response rate):

\vspace{0.5em}
\begin{center}
\small
\begin{tabular}{lccr}
\toprule
\textbf{Course} & \textbf{Responses} & \textbf{Rate} & \textbf{Effectiveness (SD)} \\
\midrule
Spring 2025 -- CMSI 2130 & 13/23 & 57\% & 4.08 (1.19) \\
Spring 2025 -- CMSI 6998 & 5/6 & 83\% & 5.00 (0.00) \\
Fall 2025 -- CMSI 2130 (Sec 01) & 11/12 & 92\% & 4.73 (0.65) \\
Fall 2025 -- CMSI 2130 (Sec 02) & 25/38 & 66\% & 4.36 (0.99) \\
\midrule
\textbf{Aggregate} & \textbf{54/79} & \textbf{68\%} & \textbf{4.43 (0.96)} \\
\bottomrule
\end{tabular}
\end{center}

\vspace{0.5em}
\noindent Highest-rated areas (aggregate):
\begin{itemize}[leftmargin=*, nosep]
\item Learning outcomes effectively addressed: 4.67/5.0 (SD: 0.73)
\item Learning outcomes clearly stated: 4.63/5.0 (SD: 0.65)
\item Instructor accessible for discussions: 4.59/5.0 (SD: 0.66)
\end{itemize}

\subsection*{Advising and Mentorship}

\subsubsection*{Graduate Students}
\begin{itemize}[leftmargin=*, nosep]
\item \textbf{Harsh Devisha} (started September 2025): Graduate Research Assistant working on cooperative mobile agent algorithms
\item \textbf{Mohammadali Khodabandehlou} (USC Ph.D. student): Co-advised on dynamic IoT task graph scheduling research, resulting in an accepted poster at SenSys 2025
\end{itemize}

\subsubsection*{Undergraduate Students}
\begin{itemize}[leftmargin=*, nosep]
\item \textbf{Jason Chamorro} (started January 2025): Research assistant on stochastic/online scheduling; lead author on paper published and presented at WORKS Workshop @ SC25 in November 2025
\item \textbf{Diego Cuadros}: Contributed to LLM-assisted endangered language translation; presented poster at LMU Undergraduate Research Symposium (March 2025) and at AmericasNLP Workshop @ NAACL 2025 (April 2025)
\item \textbf{Nick Leeds} (started February 2025): Assisting on LLM endangered language translation work
\item \textbf{Gabriel Twigg-Ho} (Fall 2024 exchange student, continued collaboration): Co-authored multiple papers on online scheduling and LLM translation
\item \textbf{Matias Martinez Gonzalez} (started September 2025): Working on SAGA scheduling library
\item \textbf{Nicholas Laus} (started September 2025): Working on SAGA scheduling library
\end{itemize}

\subsubsection*{Student Conference Presentations}
\begin{itemize}[leftmargin=*, nosep]
\item \textbf{Diego Cuadros}: Poster at LMU Undergraduate Research Symposium (March 2025); poster at AmericasNLP Workshop @ NAACL 2025 (April 2025)
\item \textbf{Jason Chamorro}: Poster at LMU Undergraduate Research Symposium (March 2025); paper presentation at WORKS Workshop @ SC25 (November 2025)
\item \textbf{Mohammadali Khodabandehlou}: Poster ``Scheduling Dynamic IoT Task Graphs'' accepted at SenSys 2025
\end{itemize}

\subsection*{Mission Contributions}
\begin{itemize}[leftmargin=*, nosep]
\item Mentored students from underrepresented groups and fostered an inclusive research environment
\item Hired research assistants through external grant funding, providing paid research opportunities
\item Supported student travel to present at conferences, including SC25 (Atlanta) through grant funding; Diego Cuadros presented at NAACL (Albuquerque) with Seaver College support
\end{itemize}

\newpage

%% ============================================================================
%% SCHOLARSHIP / RESEARCH / CREATIVE WORKS
%% ============================================================================
\section*{SCHOLARSHIP / RESEARCH / CREATIVE WORKS}

\vspace{1em}

In 2025, my research program advanced across three research areas: task graph scheduling algorithms, AI for endangered language preservation, and algorithms for cooperative mobile agents. I secured my first NSF grant as PI (\$150,000) and a second NSF conference grant (\$50,000), published and presented papers at top venues including SIROCCO, IPDPS, JSSPP, CCCG, and SC, and submitted proposals totaling over \$700,000. My research directly involves students at all levels and addresses societal challenges through technology (e.g., using AI to support Indigenous language revitalization). These efforts align with LMU's mission to address societal challenges, promote interdisciplinary collaboration, and foster student involvement in impactful research.

\subsection*{Grants Awarded}
\begin{itemize}[leftmargin=*, nosep]
\item \textbf{NSF CRII Grant} (\$150,000, July 2025): ``CRII: CSR: RUI: Novel Approaches for Task Graph Scheduling Algorithm Design, Evaluation, and Comparison'' --- My first NSF grant as PI
\item \textbf{NSF Conference Grant} (\$50,000, August 2025): ``Conference: Building Scientific and Collaborative Capacity for AI in Indigenous Language Research''
\item \textbf{OpenAI API Credits} (\$1,000, January 2025): For research in LLMs and Endangered Language Preservation
\end{itemize}

\subsection*{Proposals Submitted (Pending)}
\begin{itemize}[leftmargin=*, nosep]
\item \textbf{NSF DLI-DEL} (\$450,000 total; \$229,501 for LMU): ``LLMs and Endangered Language Preservation'' --- LMU as lead institution with me as PI (September 2025)
\item \textbf{MAIDAS Subaward} (\$150,000 over 5 years, December 2025): Co-design lead for responsible AI for Indigenous language revitalization on \$30M platform proposal
\item \textbf{Amazon AWS Think Big} (November 2025): Proposal for AI and language research
\end{itemize}

\subsection*{Proposals Submitted (Not Awarded)}
\begin{itemize}[leftmargin=*, nosep]
\item \textbf{Schmidt Sciences Humanities and AI Virtual Institute} (April 2025): Two expressions of interest submitted
\item \textbf{Imminent Grant} (\$20,000, August 2025): For endangered language translation research
\end{itemize}

\subsection*{Conference Presentations}
\begin{itemize}[leftmargin=*, nosep]
\item \textbf{SIROCCO 2025} (June 3, Delphi, Greece): Presented ``Multimodal Search on a Line''
\item \textbf{JSSPP @ IPDPS 2025} (June 4, Milan, Italy): Presented ``Evaluating the Impact of Algorithmic Components on Task Graph Scheduling''
\item \textbf{MILCOM 2025} (October 6, Los Angeles): Invited Visionary Talk on ``Rethinking Scheduling for Resilience in Mission-Critical IoT Workflows''
\item \textbf{SC25 WORKS Workshop} (November 17, Atlanta): Student Jason Chamorro presented
\end{itemize}

\subsection*{Papers Published (2025)}
\begin{enumerate}[leftmargin=*, nosep]
\item J. Coleman, D. Ivanov, E. Kranakis, D. Krizanc, and O. Morales-Ponce. ``The Power of Knowledge in Linear Search for an Escaping Target''. \textit{Journal of Computer and System Sciences (JCSS)}, December 2025.
\end{enumerate}

\subsection*{Papers Accepted for Publication}
\begin{enumerate}[leftmargin=*, nosep]
\item J. Coleman et al. ``Multimodal Search on a Line''. \textit{SIROCCO 2025}.
\item J. Coleman et al. ``Evaluating the Impact of Algorithmic Components on Task Graph Scheduling''. \textit{JSSPP @ IPDPS 2025}.
\item J. Coleman et al. ``Evaluating Scheduling Algorithms for Adaptive Orchestration in Federated Tactical Edge Cloud Environments''. \textit{ICMCIS 2025}.
\item J. Coleman et al. ``Optimal Delivery with a Faulty Drone''. \textit{CCCG 2025}.
\item J. Coleman, J. Chamorro et al. ``Adapting Classic Scheduling Heuristics for Online Execution under Uncertainty''. \textit{WORKS @ SC25}.
\item M. Khodabandehlou, J. Coleman, B. Krishnamachari. ``Scheduling Dynamic IoT Task Graphs''. \textit{SenSys 2025} (poster).
\item D. Cuadros, J. Coleman et al. ``A Chatbot for Endangered Language Research''. \textit{AmericasNLP @ NAACL 2025} (poster).
\end{enumerate}

\subsection*{Other Contributions}
\begin{itemize}[leftmargin=*, nosep]
\item \textbf{NATO Technical Report Chapter} (August 2025): Wrote chapter on ``Edge Computing at the Tactical Edge''
\item \textbf{Tutorial Accepted -- ICDCN 2025}: ``Resilient Scheduling in Distributed Systems: Benchmarking and Adversarial Analysis with SAGA''
\item \textbf{Workshop Proposal Accepted}: INFOCOM 2026 NetComm Workshop (November 2025)
\item \textbf{Adjunct Appointment at USC} (May 2025): Accepted to facilitate collaboration
\end{itemize}

\newpage

%% ============================================================================
%% SERVICE
%% ============================================================================
\section*{SERVICE}

\vspace{1em}

In 2025, I significantly expanded my service contributions across university, professional, and community domains. I took on leadership roles in multiple committees, including chairing the LMU Indigenous Working Group, joining the Seaver DEI Committee, and participating in both the CS and LMU-wide Generative AI Task Forces. My community engagement focused on Indigenous issues, including organizing events, managing the Indigenous Community Hub website, and participating in advocacy efforts. Professionally, I served on an NSF review panel, multiple program committees, and as a reviewer for top journals and conferences. These activities demonstrate my commitment to LMU's mission of promoting equity, inclusion, and service to the broader community.

\subsection*{University Service}

\subsubsection*{Committee Memberships}
\begin{itemize}[leftmargin=*, nosep]
\item \textbf{Seaver DEI Committee} (joined August 2025): Contributing to diversity, equity, and inclusion initiatives
\item \textbf{LMU Generative AI Task Force} (joined August 2025): University-wide task force on GenAI policy and practice
\item \textbf{CS GenAI Task Force} (joined July 2025): Departmental task force producing documents on GenAI in higher education
\item \textbf{Indigenous Working Group}: Active member; elected Chair in October 2025
\end{itemize}

\subsubsection*{Indigenous Working Group Leadership}
\begin{itemize}[leftmargin=*, nosep]
\item Elected Chair of the Indigenous Working Group (October 2025)
\item \textbf{Hosted Teri Red Owl} (March 20, 2025): Talk on Indigenous water rights and the Owens Valley Indian Water Commission
\item \textbf{Organized ``IN FOCUS'' Event} (December 3, 2025): ``Indigenous Representation in the Arts and Media'' featuring Emmy-nominated producer Tazbah Rose Chavez and documentarian Pamela J. Peters
\item \textbf{Managed LMU Indigenous Community Hub} (June 2025): Took over management and updated the website
\end{itemize}

\subsubsection*{Other University Engagement}
\begin{itemize}[leftmargin=*, nosep]
\item \textbf{Seaver Family Night} (October 24, 2025): Gave Lightning Lecture
\item Attended NSF CSR PI Meeting in Boca Raton, Florida (September 2025)
\end{itemize}

\subsection*{Community Engagement}

\subsubsection*{Indigenous Community Partnerships}
\begin{itemize}[leftmargin=*, nosep]
\item \textbf{N\"u\"um\"u Yadoha Language Program} (December 2025): Met with Awahusu, director of the language program in Bishop, CA, to discuss technology collaborations
\item \textbf{NSF DLI Community of Science} (May 2025): Attended Dynamic Language Infrastructure meeting
\item \textbf{AI and Indigenous Languages Workshop Committee} (September 2025): Formed and chaired organizing committee
\item \textbf{University of Arizona} (September 2025): Invited talk on AI and Indigenous Language Revitalization
\item \textbf{University of Illinois Chicago} (November 2025): Invited speaker in Lectures on Linguistics and Language Series
\end{itemize}

\subsubsection*{Advocacy}
\begin{itemize}[leftmargin=*, nosep]
\item \textbf{Tribal Settlement Letter} (August 2025): Signed letter urging Los Angeles to commit to Tribal settlement negotiations
\item \textbf{Kubishi Survey} (July 2025): IRB-approved survey on digital tools for Owens Valley Paiute Language Revitalization
\end{itemize}

\subsection*{Professional Service}

\subsubsection*{NSF Service}
\begin{itemize}[leftmargin=*, nosep]
\item \textbf{NSF Review Panel} (Summer 2025): Invited and served on review panel for the Division of Behavioral and Cognitive Sciences
\end{itemize}

\subsubsection*{Program Committee Memberships}
\begin{itemize}[leftmargin=*, nosep]
\item AAAI AISI Program Committee (AI for Social Impact track)
\item WISDOM 2025 Program Committee
\item CCGrid Artifact Evaluation Committee
\item MILCOM 2025 Session Chair: Data Integrity \& Threat Awareness
\end{itemize}

\subsubsection*{Journal Reviewing}
\begin{itemize}[leftmargin=*, nosep]
\item International Journal of Computer Applications (IJCAT)
\item Discrete Applied Mathematics
\item IEEE Transactions on Computers
\item Theoretical Computer Science
\end{itemize}

\subsection*{Consulting}
\begin{itemize}[leftmargin=*, nosep]
\item \textbf{Coinbase} (started January 2025): Consulting on using reinforcement learning to detect fraud in blockchain transactions
\end{itemize}

\newpage

%% ============================================================================
%% SIGNATURE PAGE
%% ============================================================================
\section*{FACULTY SERVICE REPORT -- CALENDAR YEAR 2025}

\vspace{2em}

The signatures below confirm that the department Chair's Written Report and Evaluation was provided to the individual faculty member on \rule{3in}{0.4pt} (MM/DD/YY) and that a FSR Discussion took place between the department Chair and individual faculty member on \rule{2in}{0.4pt} (MM/DD/YY).

\vspace{3em}

\rule{3in}{0.4pt}\\
Name of Individual Faculty Member

\vspace{2em}

\rule{3in}{0.4pt} \hfill \rule{1.5in}{0.4pt}\\
Signature of Individual Faculty Member \hfill Date

\vspace{2em}

\rule{3in}{0.4pt}\\
Name of Department Chair

\vspace{2em}

\rule{3in}{0.4pt} \hfill \rule{1.5in}{0.4pt}\\
Signature of Department Chair \hfill Date

\vspace{3em}

\noindent\underline{\textbf{OPTIONAL}}

\vspace{1em}
\noindent I received and have read my department Chair's Written Report and Evaluation but I decline the opportunity to meet with my department Chair for an FSR discussion.

\vspace{2em}

\rule{3in}{0.4pt}\\
Name of Individual Faculty Member

\vspace{2em}

\rule{3in}{0.4pt} \hfill \rule{1.5in}{0.4pt}\\
Signature of Individual Faculty Member \hfill Date

\vspace{3em}

\noindent\underline{\textbf{OPTIONAL}}

\vspace{1em}
\noindent I decline to sign this document and will provide my department Chair and Dean with a separate letter of dissent to be attached to this document.

\vspace{2em}

\rule{3in}{0.4pt}\\
Name of Individual Faculty Member

\vspace{2em}

\rule{3in}{0.4pt} \hfill \rule{1.5in}{0.4pt}\\
Signature of Individual Faculty Member \hfill Date

\end{document}
